---
title: "Main"
author: "Grace Woodhouse"
date: "04/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.retina = 3)
```

```{r packages}
library(tidyverse)
```

#Introduction
Comparison of mass between male and female Chaffs.

#Methods
Tidy the data and calculate averages.

```{r}
#read in data
file <- read.table("chaff.txt", header = TRUE)

#tidy the data
write.table(file,
quote = FALSE,
row.names = FALSE)

# library tidyverse 
library(tidyverse)
chaff2 <- pivot_longer(data = file, cols = everything(),
                       names_to = "sex", values_to = "mass")
str(chaff2)

#calculate SS(x)
sum_sq <- function(df, measure, group) {
  df %>% group_by ({{ group }}) %>% 
    summarise(ss = sum(({{measure}} - mean({{measure}}))^2))
}

sum_sq(chaff2, mass, sex)

#summarising data
chaff_summary <- chaff2 %>% 
  group_by(sex) %>%
  summarise(mean_index = mean(mass),
            n = length(mass),
            sd = sd(mass),
            se = sd/sqrt(n))
str(chaff_summary)
#create a function
```

#Results 
The difference in masses by sex. The *SS(x)* values for *females* is **86.8320**, whilst for *males* it is **87.8975**.
Summary of data shows a *mean* of **20.48** for *females* and **22.28** for *males*. *standard deviation* for *males* is **2.15**  and *standard error* of **0.481**. 
*Females* have a *standard deviation* of **2.14** and a *standard error* of **0.478**.

#Discussion
What are the implications of this difference.